Characteristic polynomials of p-adic matrices

### 2017-02-04 charpoly/charpoly.tex

\subsection*{Notation} Throughout the paper, $K$ will refer to a complete,
discrete valuation field, $\val : K \twoheadrightarrow \Z \cup \{+\infty\}$ to its valuation,
$\OK$ its ring of integers and $\pi$ a uniformizer. \todo{$\softO$, $\omega$, scalar matrices and $I_n$, $\sigma_1(M), \dots, \sigma_n(M)$}

\section{Theoretical study}

>>>>

In Section \ref{sec:theo_study}, we study the
differential of the characteristic polynomial so as
to get optimal information on precision 
and a compact writing of this differential.
Then, in Sections \ref{sec:diffHess} and \ref{sec:diffFrob}
we propose algorithms to compute this differential
either through Hessenberg or going through
some Frobenius normal form.
Finally, we propose in Section \ref{sec:optjagged}
algorithms to compute the optimal precision
coefficient-wise on the characteristic polynomial
and on some eigenvalues along with
numerical evidence of the behaviour of the computation
of the characteristic polynomial.

\subsection*{Notation} Throughout the paper, $K$ will refer to a complete,
discrete valuation field, $\val : K \twoheadrightarrow \Z \cup \{+\infty\}$ to its valuation,
$\OK$ its ring of integers and $\pi$ a uniformizer. 
We will write that $f(n)=\softO (g(n))$ if there exists some
$k \in \mathbb{N}$ such that $f(n)=O(g(n) \log (n)^k.$
We fix an $\omega \in \mathbb{R}$ such that the multiplication
of two matrices over a ring is in $O(n^\omega)$ operations in the
ring. Currently, the smallest proved $\omega$ is less than
$2.3728639 $ thanks to \cite{legall:14a}. 
$I_n$ will denote the identity matrix of rank $n$ in $M_n(K).$
When there is no ambiguity, we will drop this $I_n$
for scalar matrices, \textit{e.g.} for $\lambda \in K$
and $M \in M_n (K),$ $\lambda-M$ denotes $\lambda I_n -M.$

\section{Theoretical study}
\label{sec:theo_study}
